Hypertension and microbiome

### 2019-02-05 articletwo.Rmd
Minor

# Running at

@@

```{r Running at}
now <- ifelse(exists('now'),now, format(Sys.time(), '%Y%m%d-%H%M%S'))
```

@@

```{r Remove temporary data, include = FALSE, cache = FALSE, eval = FALSE}
unlink("rds", recursive=TRUE)
unlink("cache", recursive=TRUE)
```

>>>>

# Command line arguments

@@

```{r Running at}
args <- R.utils::commandArgs(trailingOnly = TRUE, asValues = TRUE, unique = TRUE)
now <- ifelse("time" %in% names(args),
              args$time,
              format(Sys.time(), '%Y%m%d-%H%M%S'))

if("clean" %in% names(args)) {
    unlink("rds", recursive=TRUE)
    unlink("cache", recursive=TRUE)
}
```

@@
